Wavelength convergence of the $\exb$ staircase pattern in flux tube simulations of ion temperature gradient driven turbulence

### 2023-03-19 briefcommunicaton/briefcommunication.tex
#37: Hamada coord with explanation, Readjust diagnostics, N_\psi and N_\zeta, \rho_th to \rho

\newcommand{\wexb}{\omega_{\mathrm{\:E \times B}}}
\newcommand{\hatwexb}{\widehat{\omega}_{\mathrm{\:E \times B}}}
\newcommand{\exb}{\mathrm{\:E}\times\mathrm{B}}
\newcommand{\hatwexbkvec}{\widehat{\omega}_{\mathrm{\:E \times B},\mathbf{k}}}
\newcommand{\NR}{N_\mathrm{R}}
\newcommand{\NB}{N_\mathrm{B}}
\newcommand{\rlt}{R/L_T}
\newcommand{\rhoth}{\rho_\mathrm{th}}
\newcommand{\vth}{v_{\mathrm{th}}}

@@

The $\exb$ staircase pattern is manifest as radial structure formation in the $\exb$ shearing rate defined by\cite{rath2016, doi:10.1063/1.3005380, rath2016, peeters2016}
\begin{equation}
	\wexb = \frac{1}{2} \frac{\partial^2 \langle \Phi \rangle}{\partial \psi^2},
	\label{eq:shearingrate}
\end{equation}
\increasecounter{eq}{1}{1}
where $\langle \Phi \rangle$ is the zonal electrostatic potential normalized by $\rho_\ast T/e$ ($\rho_\ast = \rhoth/R$ is the thermal Larmor radius normalized with the major radius $R$, $T$ is a temperature, $e$ is the elementary charge) and $\psi$ is the radial coordinate that labels the flux surfaces normalized by $\rhoth$.

The E$\times$B shearing rate $\wexb$ is the radial derivative of the advecting zonal flow velocity \cite{doi:10.1063/1.871313, doi:10.1063/1.872847} and quantifies the zonal flow induced shearing of turbulent structures \cite{doi:10.1063/1.859529, doi:10.1063/1.871313, doi:10.1063/1.872367}. 
Here, the zonal potential is estimated from the electrostatic potential $\phi$ on the two-dimensional $\psi$-$\zeta$-plane at the low field side according to
\begin{equation}
\langle \Phi \rangle = \frac{1}{l_\zeta} \int_0^{l_\zeta} \mathrm{d}\zeta ~ \phi(\psi,\zeta,s=0).
\end{equation}
In order to diagnose the temporal evolution of the staircase pattern and to obtain an estimate of its amplitude the radial Fourier transform of the $\exb$ shearing rate is considered. 
It is defined by
\begin{equation}
	\wexb = \sum_{k_j} \hatwexb(k_j,t) \times \exp(\mathrm{i} k_j \psi),
	\label{eq:shearingrate_fourier}
\end{equation}
\increasecounter{eq}{1}{1}
were $\hatwexb$ is the complex Fourier coefficient and 
% use j as zonal flow mode number to distinguish it from the imaginary unit i
\begin{equation}
	k_\mathrm{j} = \frac{2\pi \mathrm{j}}{l_\psi}
\end{equation}
\increasecounter{eq}{1}{1}
% explicitly introduce the terms zonal flow wave vector and zonal flow mode number for later usage
defines the zonal flow wave vector with the zonal flow mode number $j$ ranging in $-(N_\psi -1)/2 \leq j \leq (N_\psi -1)/2 $.
% define the zonal flow modes' amplitude in terms of the shearing rate
Based on the definitions above, the shear carried by the zonal flow mode with wave vector $k_j$ is defined by $|\hatwexb|_{k_\mathrm{j}} = 2 |\hatwexb|$. 
% introduces the term basic mode of the pattern for later usage
In general, the zonal flow mode that dominates the $\exb$ staircase pattern, \textemdash also referred to as the \textit{basic mode } of the pattern in this work \textemdash exhibits the maximum amplitude in the spectrum $|\hatwexb|_{k_\mathrm{j}}$.

@@

Consistent with Ref.~\cite{peeters2016} the turbulence level is quantified by the turbulent heat conduction coefficient $\chi$, which is normalized by $\rhoth^2 \vth/R$ ($\vth = \sqrt{2 T/m}$ is the thermal velocity and $m$ is the mass) throughout this work. Furthermore, quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities from Ref (\textbf{?}).\bigskip

>>>>

\newcommand{\wexb}{\omega_{\mathrm{\:E \times B}}}
\newcommand{\hatwexb}{\widehat{\omega}_{\mathrm{\:E \times B}}}
\newcommand{\exb}{\mathrm{\:E}\times\mathrm{B}}
\newcommand{\hatwexbkvec}{\widehat{\omega}_{\mathrm{\:E \times B},\mathbf{k}}}
%\newcommand{\NR}{N_\mathrm{R}}
%\newcommand{\NB}{N_\mathrm{B}}
\newcommand{\NR}{N_\psi}
\newcommand{\NB}{N_\zeta}
\newcommand{\rlt}{R/L_T}
%\newcommand{\rhoth}{\rho_\mathrm{th}}
\newcommand{\rhoth}{\rho}
\newcommand{\vth}{v_{\mathrm{th}}}

@@

The $\exb$ staircase pattern is manifest as radial structure formation in the $\exb$ shearing rate defined by\cite{rath2016, doi:10.1063/1.3005380, rath2016, peeters2016}
\begin{equation}
	\wexb = \frac{1}{2} \frac{\partial^2 \langle \phi \rangle}{\partial \psi^2},
	\label{eq:shearingrate}
\end{equation}
\increasecounter{eq}{1}{1}
where $\langle \phi \rangle$ is the zonal electrostatic potential normalized by $\rho_\ast T/e$ ($\rho_\ast = \rhoth/R$ is the thermal Larmor radius normalized with the major radius $R$, $T$ is the temperature, $e$ is the elementary charge) and $\psi$ is the radial coordinate that labels the flux surfaces normalized by $\rhoth$. 
The zonal potential is estimated from the electrostatic potential $\phi$ on the two-dimensional $\psi$-$\zeta$-plane at the low field side according to
\begin{equation}
\langle \phi \rangle = \frac{1}{l_\zeta} \int_0^{l_\zeta} \mathrm{d}\zeta ~ \phi(\psi,\zeta,s=0),
\end{equation}
where $\zeta$ labels the field lines and is an approximate binormal or toroidal coordinate, and $s$ parameterizes the length along the field lines and represents a poloidal coordinate which represents together with the radial coordinate $\psi$ the Hamada coordinates $(\psi,\zeta,s)$. \cite{rath2021} (\textbf{REFERENCE Hamada})
The E$\times$B shearing rate $\wexb$ is the radial derivative of the advecting zonal flow velocity \cite{doi:10.1063/1.871313, doi:10.1063/1.872847} and quantifies the zonal flow induced shearing of turbulent structures \cite{doi:10.1063/1.859529, doi:10.1063/1.871313, doi:10.1063/1.872367}.

In order to diagnose the temporal evolution of the staircase pattern and to obtain an estimate of its amplitude the radial Fourier transform of the $\exb$ shearing rate is considered. 
It is defined by
\begin{equation}
	\wexb = \sum_{k_j} \hatwexb(k_j,t) \, \exp(\mathrm{i} k_j \psi),
	\label{eq:shearingrate_fourier}
\end{equation}
\increasecounter{eq}{1}{1}
where $\hatwexb$ is the complex Fourier coefficient and \linebreak $k_\mathrm{j} = 2\pi \mathrm{j}/l_\psi$
% explicitly introduce the terms zonal flow wave vector and zonal flow mode number for later usage
defines the zonal flow wave vector with the zonal flow mode number $j$ ranging in $-(N_\psi -1)/2 \leq j \leq (N_\psi -1)/2 $.
% define the zonal flow modes' amplitude in terms of the shearing rate
Based on the definitions above, the shear carried by the zonal flow mode with wave vector $k_j$ is defined by $|\hatwexb|_{k_\mathrm{j}} = 2 |\hatwexb|$.

% introduces the term basic mode of the pattern for later usage
In general, the zonal flow mode that dominates the $\exb$ staircase pattern, \textemdash also referred to as the \textit{basic mode } of the pattern in this work \textemdash exhibits the maximum amplitude in the spectrum $|\hatwexb|_{k_\mathrm{j}}$.

@@

Consistent with Ref.~\cite{peeters2016} the turbulence level is quantified by the turbulent heat conduction coefficient $\chi$, which is normalized by $\rhoth^2 \vth/R$ ($\vth = \sqrt{2 T/m}$ is the thermal velocity and $m$ is the mass) throughout this work. Furthermore, quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities from Ref (\textbf{REFERENCE Quantities}).\bigskip
